\Large Taking uncertainty seriously \newline \normalsize A Bayesian approach to word embedding bias estimation

### 2022-03-20 presentations/presentationBoston/presentationBoston.Rmd
Adds the rest of violins

>>>>

### No principled interpretation - visualization 1
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "90%"}
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(kableExtra)
library(magrittr)
library(ggplot2)
library(ggpubr)
library(ggExtra)
library(ggthemes)
library(ggforce)
library(latex2exp)

religionReddit <- read.csv("../../datasets/religionReddit.csv")[-1]

cosAssReligion <- religionReddit['cosine_similarity'][which(religionReddit$connection == 'associated'),]
cosDiffReligion <- religionReddit['cosine_similarity'][which(religionReddit$connection == 'different'),]
cosNoneReligion <- religionReddit['cosine_similarity'][which(religionReddit$connection == 'none'),]
cosHumReligion <- religionReddit['cosine_similarity'][which(religionReddit$connection == 'human'),]

ggplot(religionReddit, aes(x = connection, y = cosine_similarity, fill = connection, color = connection))+
  geom_violin(alpha = .5)+coord_flip()+
  geom_vline(xintercept = .14) + geom_hline(yintercept = -.14, color = "grey") +
  ylab("similarity")+theme_tufte()+ geom_hline(yintercept = .14, color = "grey")+
  ggtitle("Religion: empirical distribution of cosine similarity")+
  annotate(geom = "label", x = 4, y = 0, label = "56%")+
  annotate(geom = "label", x = 3, y = 0, label = "55%")+
  annotate(geom = "label", x = 2, y = 0, label = "43%")+
  annotate(geom = "label", x = 1, y = 0, label = "36%")
```

### No principled interpretation - visualization 2

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "90%"}
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(kableExtra)
library(magrittr)
library(ggplot2)
library(ggpubr)
library(ggExtra)
library(ggthemes)
library(ggforce)
library(latex2exp)

raceReddit <- read.csv("../../datasets/raceReddit.csv")[-1]

cosAssReligion <- raceReddit['cosine_similarity'][which(raceReddit$connection == 'associated'),]
cosDiffReligion <- raceReddit['cosine_similarity'][which(raceReddit$connection == 'different'),]
cosNoneReligion <- raceReddit['cosine_similarity'][which(raceReddit$connection == 'none'),]
cosHumReligion <- raceReddit['cosine_similarity'][which(raceReddit$connection == 'human'),]

ggplot(raceReddit, aes(x = connection, y = cosine_similarity, fill = connection, color = connection))+
  geom_violin(alpha = .5)+coord_flip()+
  geom_vline(xintercept = .11) + geom_hline(yintercept = -.11, color = "grey") +
  ylab("similarity")+theme_tufte()+ geom_hline(yintercept = .11, color = "grey")+
  ggtitle("Race: empirical distribution of cosine similarity")+
  annotate(geom = "label", x = 4, y = 0, label = "46%")+
  annotate(geom = "label", x = 3, y = 0, label = "67%")+
  annotate(geom = "label", x = 2, y = 0, label = "39%")+
  annotate(geom = "label", x = 1, y = 0, label = "33%")
```

### No principled interpretation - visualization 3

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "90%"}
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(kableExtra)
library(magrittr)
library(ggplot2)
library(ggpubr)
library(ggExtra)
library(ggthemes)
library(ggforce)
library(latex2exp)

genderReddit <- read.csv("../../datasets/genderReddit.csv")[-1]

cosAssReligion <- genderReddit['cosine_similarity'][which(genderReddit$connection == 'associated'),]
cosDiffReligion <- genderReddit['cosine_similarity'][which(genderReddit$connection == 'different'),]
cosNoneReligion <- genderReddit['cosine_similarity'][which(genderReddit$connection == 'none'),]
cosHumReligion <- genderReddit['cosine_similarity'][which(genderReddit$connection == 'human'),]

ggplot(genderReddit, aes(x = connection, y = cosine_similarity, fill = connection, color = connection))+
  geom_violin(alpha = .5)+coord_flip()+
  geom_vline(xintercept = .38) + geom_hline(yintercept = -.38, color = "grey") +
  ylab("similarity")+theme_tufte()+ geom_hline(yintercept = .38, color = "grey")+
  ggtitle("Gender: empirical distribution of cosine similarity")+
  annotate(geom = "label", x = 4, y = 0, label = "96%")+
  annotate(geom = "label", x = 3, y = 0, label = "87%")+
  annotate(geom = "label", x = 2, y = 0, label = "53%")+
  annotate(geom = "label", x = 1, y = 0, label = "47%")
```

### 2022-03-20 presentations/presentationBoston/presentationBoston.tex
Adds the rest of violins

@@

\begin{center}\includegraphics[width=0.7\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-6-1} \end{center}
\normalsize

@@

\begin{center}\includegraphics[width=0.7\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-8-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-9-1} \end{center}
\vspace{1mm}
\footnotesize

@@

\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-11-1} \end{center}
\vspace{1mm}
\footnotesize

@@

\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-13-1} \end{center}
\vspace{1mm}
\footnotesize

>>>>

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-7}{}
\begin{block}{No principled interpretation - visualization 1}
\protect\hypertarget{no-principled-interpretation---visualization-1}{}
\begin{center}\includegraphics[width=0.9\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-6-1} \end{center}
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-8}{}
\begin{block}{No principled interpretation - visualization 2}
\protect\hypertarget{no-principled-interpretation---visualization-2}{}
\begin{center}\includegraphics[width=0.9\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-7-1} \end{center}
\end{block}
\end{frame}

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-9}{}
\begin{block}{No principled interpretation - visualization 3}
\protect\hypertarget{no-principled-interpretation---visualization-3}{}
\begin{center}\includegraphics[width=0.9\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-8-1} \end{center}
\end{block}
\end{frame}

@@

\begin{center}\includegraphics[width=0.7\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-9-1} \end{center}
\normalsize

@@

\begin{center}\includegraphics[width=0.7\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-11-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-12-1} \end{center}
\vspace{1mm}
\footnotesize

@@

\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-14-1} \end{center}
\vspace{1mm}
\footnotesize

@@

\begin{center}\includegraphics[width=0.8\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-16-1} \end{center}
\vspace{1mm}
\footnotesize
